Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
wip

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$,
	 then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with  cost zero.
	Therefore in this case,
	$\OPT(\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as defined previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$  analogously.
	Then,
	$\OPT(R_t) =\OPT (\sigma_{\{u,w\}}) 
	+ \OPT(\sigma_{\{u,v\}}) $.
	If \OPT has both pairs separated during their respective intervals,
	then obviously it pays $2\lambda$ during those intervals.
	Note that \OPT cannot have both pairs collocated at the same time.
%	However, it can have one of the pairs already collocated prior to its respective interval.
	Let us assume \OPT has one of the pairs,
	e.g.~$\{u,v\}$,
	 collocated already prior its respective interval, $(t',t]$,
	 and keeps it so during the interval.
	 Then it pays zero while serving $\sigma_{\{u,v\}}$.
	Hence,
	it must pay $\alpha$ for collocating the other pair, in this case $\{u,w\}$,
	or (resp., and) it pays (resp., up to) $\lambda$ for serving (resp., some of) requests in $\sigma_{\{u,w\}}$ \maciek{Rewrite without these resp.s}. 
	Therefore in any case,
	$\OPT(R_t) \geq  \min{\{ \lambda,\alpha \}} = \alpha$.

	It remains to bound the cost  incurred by \OPT due to requests to $\{u,v\}$ that do not lead to its collocation until the end of the sequence at $t=m$.
	We bound the cost analogously to the case where \RM collocates $\{u,v\}$.
	If $\{u,v\}$ is not collocated in the initial matching
	and \RM never collocates it,
	then $ C^{m}_{ \{u,v\} } =| \sigma_{\{u,v\}}[1,m] |$.
	\OPT pays
	$\OPT(\sigma_{\{u,v\}}[1,m]) 
	\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
	for collocating this pair or (and) paying for (resp.~some of) requests in $\sigma_{\{u,v\}}[1,m]$.
	Else,
	either $\{u,v\}$ is collocated in the initial matching
	or \RM collocates it at some point.
	Then there exists an intersecting pair $\set{u,w}$
	that is collocated by \RM at $t' < m$,
	separating $\{u,v\}$.
	We define times $t'' < t' < m$ similarly to the former case \maciek{doing thing "similarly" is a trap zone in proofs, and we should avoid even suggesting it. I think that here you mean defining exactly the same.}.
	Let $R^*_{\{u,v\}} := \sigma_{\{u,w\}} (t'',t'] \cup \sigma_{\{u,v\}} (t',m]$.
	Then,
	\OPT must pay for collocating at least one pair or (and) serving requests 
	to the other pair remotely.
	Thus,
	$\OPT (R^*_{\{u,v\}}) 
	\geq  \min{ \{ C^{m}_{ \{u,v\}}, \alpha \}}$.

>>>>

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$,
	 then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with  cost zero.
	Therefore in this case,
	$\OPT(\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as defined previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$  analogously.
	Then,
	$\OPT(R_t) =\OPT (\sigma_{\{u,w\}}) 
	+ \OPT(\sigma_{\{u,v\}}) $.
	If \OPT has both pairs separated during their respective intervals,
	then obviously it pays $2\lambda$ during those intervals.
	Note that \OPT cannot have both pairs collocated at the same time.
%	However, it can have one of the pairs already collocated prior to its respective interval.
	Let us assume \OPT has one of the pairs,
	e.g.~$\{u,v\}$,
	 collocated already prior its respective interval, $(t',t]$,
	 and keeps it so during the interval.
	 Then it pays zero while serving $\sigma_{\{u,v\}}$.
	Hence,
	it must pay $\alpha$ for collocating the other pair, in this case $\{u,w\}$,
	or (resp., and) it pays (resp., up to) $\lambda$ for serving (resp., some of) requests in $\sigma_{\{u,w\}}$ \maciek{Rewrite without these resp.s. Also, see the comment on "or (and)" below}. 
	Therefore in any case,
	$\OPT(R_t) \geq  \min{\{ \lambda,\alpha \}} = \alpha$.

	It remains to bound the cost  incurred by \OPT due to requests to $\{u,v\}$ that do not lead to its collocation until the end of the sequence at $t=m$.
	We bound the cost analogously to the case where \RM collocates $\{u,v\}$.
	If $\{u,v\}$ is not collocated in the initial matching
	and \RM never collocates it,
	then $ C^{m}_{ \{u,v\} } =| \sigma_{\{u,v\}}[1,m] |$.
	\OPT pays
	$\OPT(\sigma_{\{u,v\}}[1,m]) 
	\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
	for collocating this pair or (and) paying for (resp.~some of) requests in $\sigma_{\{u,v\}}[1,m]$.
	Else,
	either $\{u,v\}$ is collocated in the initial matching
	or \RM collocates it at some point.
	Then there exists an intersecting pair $\set{u,w}$
	that is collocated by \RM at $t' < m$,
	separating $\{u,v\}$.
	We define times $t'' < t' < m$ similarly to the former case \maciek{doing thing "similarly" is a trap zone in proofs, and we should avoid even suggesting it. I think that here you mean defining exactly the same.}.
	Let $R^*_{\{u,v\}} := \sigma_{\{u,w\}} (t'',t'] \cup \sigma_{\{u,v\}} (t',m]$.
	Then,
	\OPT must pay for collocating at least one pair or (and) \maciek{"or (and)" usually should be "and possibly". Does this make sense here?} serving requests 
	to the other pair remotely.
	Thus,
	$\OPT (R^*_{\{u,v\}}) 
	\geq  \min{ \{ C^{m}_{ \{u,v\}}, \alpha \}}$.
